\ifczech

\else

\textbf{Idleforces} \hfill \textit{A Codeforces simulator idle game} \par
\textit{Hosted at \href{https://idleforces.netlify.app/}, on \href{https://github.com/Idleforces/idleforces}{GitHub} under an organization}
\begin{itemize}
    \item Used React for interactivity, Redux for in-session state management and localStorage for persistence.
    \item Designed a complex 10+ parameter model for a Codeforces contest, handling 1000+ simulated users gathered from the Codeforces API at the time.
    \item Came up with a 10+ parameter model for player skill that can be honed by participating in contests or by reading books.
    \item Implemented a string-based import / export save system.
\end{itemize}

\textbf{Carcassonne Czechia} \hfill \textit{A website of the Czech national team in Carcassonne} \par
\textit{Hosted at \href{https://carcassonne-czechia.netlify.app/}, on \href{https://github.com/Carcassonne-Czechia/carcassonne-czechia}{GitHub} under an organization}
\begin{itemize}
    \item Used Primereact UI library to design a fully-responsive and consistent website.
    \item Used React to interactively display tournament statistics.
    \item Minimized manual updating and maintenance needed by employing a sensible structure combined with GitHub Actions.
\end{itemize}

\textbf{Figgie clone} \hfill \textit{A card game designed by Jane Street} \par
\begin{itemize}
    \item Used Node.js and PostgreSQL database on the backend, React on the frontend connected by Websockets to build a fully-functional Figgie client.
\end{itemize}
\fi